Manuscript figures

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 6 for revision

ggsave(here('docs/figures/curves_k15_only_final_mod_v2.png'),
       curves,
       width = 7, height = 5, dpi = 300)
```

>>>>

# Figure 6, line art
# Double figure (7 in in width), 7000 * 5000 at 1000 dpi
ggsave(here('docs/figures/figure6_training_curves.tiff'),
       curves, bg = "white", width = 7, height = 5, dpi = 1000)
```
